Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-16 analysis/paper/paper.Rmd
Add captions to figures

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_f1)) + 
  scale_colour_grey() +
  ggtitle("Code")

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_g1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='I am so tired', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_h1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

>>>>

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. Intervals in grey have a median value less than that of *Phytopathology*, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*. Intervals in black have a median value that is greater than that of *Phytopathlogy*, the base level for the analysis and articles in these journals could be more likely to share data or code than those found in *Phytopathology*.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_f1)) +
  scale_colour_grey() +
  ggtitle("Code")

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_g1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='95% credible interval for the probability associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public.', cache=FALSE, fig.env='figure'}
a <- plot(parameters(m_h1), show_lables = TRUE) + 
  scale_colour_grey() +
  ggtitle("Code")
